Responses to the Reviewers' Comments

### 2024-10-03 Response/Paper_Res.tex
Rev_V5.0

%	\begin{table*}[htbp]\textcolor{blue}{
%		\renewcommand{\arraystretch}{0.6}
%		\captionsetup{name=TABLE}
%		\caption{Comparison of Related Works Characteristic\vspace{4mm}}
%		\scalebox{0.7}{%
%			\begin{tabular}{ lp{3.4cm}p{4.5cm}p{5.2cm}p{1.7cm}p{3cm}p{4.6cm}l} 
%				\toprule
%				\textbf{Paper} & \textbf{Scenario} &  \textbf{Problem} &  \textbf{Objective} &  \textbf{Model} & \textbf{Method} &  \textbf{Drawbacks}  \\ \midrule
%				\cite{liao2023online} & Queuing-based MEC & Online computation offloading & Minimize computation delay and energy consumption & MDP & DDQN & Only for a singel MEC system model  \\\midrule
%				\cite{zhou2021deep} & heterogeneous MEC & Resource allocation and computation offloading & Minimize energy consumption of the entire system & MDP & DDQN & Only for a singel MEC system model \\\midrule				
%				\cite{huang2019deep} & Wireless-powered MEC & Computation offloading and resource allocations & Maximize computation rate & MIP & DQN & Not consider delay-sensitive tasks \\\midrule
%				\cite{wu2024privacy} & MEC-based IIoT  & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service. & MDP & Multi-agent DDPG & Not take user's deman into consideration \\\midrule
%				\cite{zhao2019deep} & MEC & User association and resource allocation & Optimize downlink utility & MDP & Multi-agent D3QN & Not consider system delay and energy consumtion \\\midrule
%				\cite{sun2024hierarchical} & MEC & Computation offloading and service caching & Minimize average service delay & MDP & hierarchical DRL & Not consider system energy consumtion \\\midrule
%				\cite{wu2023computation} & SDN-based MEC & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & MDP & MARL & Not consider tasks with maximum delay tolerance\\\midrule
%				\cite{dai2020edge} & MEC & Resource allocation and computation offloading & Minimize energy consumption & MDP & DDPG & Not take user's deman into consideration \\\midrule
%				\cite{liu2021learn} & MEC & Resource allocation and computation offloading & Minimize execution cost & POMDP & MADRL &  Not consider delay-sensitive tasks \\\midrule
%				\cite{gong2022edge} & MEC-based IIoT & Resource allocation and computation offloading & Minimize task computation delay and energy consumption & MDP & DRL & Not take user's deman into consideration\\\midrule
%				\cite{gao2022large} & Queuing-based heterogeneous MEC & Decentralized computation offloading & Optimize system cost and completion rates & MDP & Multi-agent DDPG & Not take user's deman into consideration \\\midrule
%				\cite{9253665} &  Queuing-based MEC &  Computation offloading & Minimize drop rate and computation delay. & MDP & D3QN + LSTM & Not consider system energy consumtion\\\midrule
%				\cite{wu2024combining} & Queuing-based IIoT MEC & Privacy aware computation offloading & Optimization of computation rate and energy consumption & MDP & DDPG  & Not take user's deman into consideration \\\midrule
%				\cite{wu2023multi} & Queuing-based IIoT MEC & Computation offloading & Optimize delay and energy consumption & POMDP & Multi-agent DQN&  Not consider tasks with maximum delay tolerance \\\midrule
%				\cite{huang2021deadline} & Queuing-based MEC & Computation offloading & Optimize drop rate and energy consumption & POMDP & DDPG & Not consider computation delay \\ \midrule
%				\cite{Bolourian-WCL24} & Queuing-based MEC with EHs& Energy harvesting  computation offloading & Minimize drop rate and energy consumption. & MDP  & DQN & Not consider computation delay  \\\midrule
%				QECO &  Queuing-based MEC &  Computation offloading & Maximize the QoE of each MD individually &MDP & D3QN + LSTM & \\
%				\toprule
%		\end{tabular}}
%		\label{table1}}
%\end{table*}

@@

\begin{itemize}
	\item \textit{Task Offloading Problem in the MEC System:} We formulate the task offloading problem as an MDP for time-sensitive tasks. This approach takes into account the dynamic nature of workloads at the ENs and concentrates on providing high performance in the MEC system while maximizing the long-term QoE.

	\item \textit{DRL-based Offloading Algorithm:} To address the problem of long-term QoE maximization, we focus on task completion, task delay, and energy consumption to quantify the MDs' QoE. We propose QECO algorithm based on DRL that empowers each MD to make offloading decisions independently, without prior knowledge of the other MDs' tasks and offloading models. With a focus on the MD's battery level, our approach leverages deep Q-network (DQN) \cite{mnih2015human} and long short-term memory (LSTM) \cite{hochreiter1997long} to prioritize and strike an appropriate balance between QoE factors. We also analyze the training convergence and complexity of the proposed algorithm.

	\item \textit{Performance Evaluation:} We conduct comprehensive experiments to evaluate the QECO's performance as well as its training convergence under different computation workloads. The results demonstrate that our algorithm quickly converges and effectively utilizes the processing capabilities of MDs and ENs, resulting in substantial improvement of at least 37\% in average QoE. This advantage is achieved through a 14\% increase in the number of completed tasks, along with 9\% and 6\% reductions in task delay and energy consumption, respectively, when compared to the potential game-based offloading algorithm (PGOA) \cite{yang2018distributed} and several benchmark methods.

@@

\section{System Model} 
\label{section:II}
\label{sec:latexhints}
% Required for proper example rendering in the compiled PDF
\newcount\LTGbeginlineexample
\newcount\LTGendlineexample
\newenvironment{ltgexample}%
{\LTGbeginlineexample=\numexpr\inputlineno+1\relax}%
{\LTGendlineexample=\numexpr\inputlineno-1\relax%
	%
	\tcbinputlisting{%
		listing only,
		listing file=\currfilepath,
		colback=green!5!white,
		colslot=green!25,
		coltitle=black!90,
		coltext=black!90,
		left=8mm,
		title=Corresponding \LaTeX{} code of \texttt{\currfilepath},
		listing options={%
			slot=none,
			language={[LaTeX]TeX},
			escapeinside={},
			firstline=\the\LTGbeginlineexample,
			lastline=\the\LTGendlineexample,
			firstnumber=\the\LTGbeginlineexample,
			basewidth=.5em,
			aboveskip=0mm,
			belowskip=0mm,
			numbers=left,
			xleftmargin=0mm,
			numberstyle=\tiny,
			numbersep=8pt%
		}
	}
}%
We investigate a MEC system consisting of a set of MDs denoted by $\mathcal{I} = \{1, 2, ..., I\}$, along with a set of ENs denoted by $\mathcal{J} = \{1, 2, ..., J\}$, where $I$ and $J$ represent the number of MDs and ENs, respectively. We regard time as a specific episode containing a series of $T$ time slots denoted by $\mathcal{T} = \{1, 2, \ldots, T\}$, each representing a duration of $\tau$ seconds. As shown in Fig.~\ref{fig1}, we consider two separate queues for each MD to organize tasks for local processing or dispatching to ENs, operating in a first-in-first-out (FIFO) manner. The MD's scheduler is responsible for assigning newly arrived tasks to each of the queues at the beginning of the time slot. On the other hand, we assume that each EN $j \in \mathcal{J}$ consists of $I$ FIFO queues, where each queue corresponds to an MD $i \in \mathcal{I}$. When each task arrives at an EN, it is enqueued in the corresponding MD's queue. %We assume that if a task is completed in a certain time slot, the next task in the queue will start its operation at the beginning of the next time slot.

\begin{figure}
	\captionsetup{name=Fig.}
	\centering
	\includegraphics[width=.7\linewidth]{ queue}
	\vspace*{-1mm}
	\caption{An illustration of MD $i \in \mathcal{I}$ and EN $j \in \mathcal{J}$ in the MEC system.}
	\vspace*{-3mm}
	\label{fig1}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{ DQN}
	\captionsetup{name=Fig.}

	\caption{The neural network of MD $i \in \mathcal{I}$, which characterize the Q-value of each action $\boldsymbol{a} \in \mathcal{A}$ under state $\boldsymbol{s}_i(t) \in \mathcal{S}$.}
	\vspace*{-4.5mm}
	\label{DQN}
\end{figure}

@@

@@

	\item \textbf{PGOA~\cite{yang2018distributed}:} This existing method is a distributed optimization algorithm designed for delay-sensitive tasks in an environment where MDs interact strategically with multiple ENs. We select PGOA as a benchmark method due to its similarity to our work.
\end{enumerate}

@@

%This represents a notable enhancement of 77\% and 16\% over LC and PGOA, respectively. This improvement is attributed to our algorithm's ability to reduce each user-associated cost regarding \eqref{28}, while striving to increase the number of completed tasks. As shown in Figs. \ref{chart0} (b), the converged QECO algorithm decreases the average cost by 38\% compared to RD and 25\% compared to PGOA.

@@

We first evaluate the number of completed tasks when comparing our proposed QECO algorithm with the other four schemes. As illustrated in Fig.~\ref{chart1} (a), the QECO algorithm consistently outperforms the benchmark methods when we vary the task arrival rate. At a lower task arrival rate (i.e., 50), most of the methods demonstrate similar proficiency in completing tasks. However, as the task arrival rate increases, the efficiency of QECO becomes more evident. Specifically, when the task arrival rate increases to 250, our algorithm can increase the number of completed tasks by 73\% and 47\% compared to RD and PGOA, respectively.
Similarly, in Fig.~\ref{chart1} (b), as the number of MDs increases, QECO shows significant improvements in the number of completed tasks compared to other methods, especially when faced with a large number of MDs. When there are 110 MDs, our proposed algorithm can effectively increase the number of completed tasks by at least 34\% comparing with other methods. This achievement is attributed to the QECO's ability to effectively handle unknown workloads and prevent congestion at the ENs.

Figs.~\ref{chart2} (a) and ~\ref{chart2} (b) illustrate the overall energy consumption for different values of task arrival rate and the number of MDs, respectively. At the lower task arrival rate, the total energy consumption of all methods is close to each other. The total energy consumption increases when we have a higher task arrival rate.  
%When the task arrival rate increases, the total energy consumption of each method increases differently. It can be found that the production of more computational tasks leads to a continuous increase in energy consumption until the capacity is saturated, and the energy consumption remains constant at its maximum. The QECO algorithm takes into account the battery level of the MD in its decision-making process. 
As can be observed from Fig.~\ref{chart2} (a), at task arrival rate 450, QECO effectively reduces overall energy consumption by 18\% and 15\% compared to RD and PGOA, respectively, as it takes into account the battery level of the MD in its decision-making process. However, it consumes more energy compared to LC and FO because they do not utilize all computing resources. In particular, LC only uses the MD's computational resources, while FO utilizes the allocated EN computing resources.

\begin{figure}[tbp]
	\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.34\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ completed_tasks_1} 
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.34\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ completed_tasks_2}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}
	%\vspace{-0.65cm}
	\caption{The number of completed tasks under different computation workloads: (a) task arrival rate; (b) the number of MDs.}
	\label{chart1}
\end{figure}

\begin{figure}[tbp]
	\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.340\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ energy_1} 		
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	%\hspace{-0.2cm}
	\begin{minipage}[b]{0.340\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ energy_2}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}
	%\vspace{-0.7cm}
	\caption{The overall energy consumption under different computation workloads: (a) task arrival rate; (b) the number of MDs.}
	\label{chart2}
\end{figure}

\begin{figure}[t]
	\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.340\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ delay_1} 		
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.340\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ delay_2}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}
	%\vspace{-0.7cm}
	\caption{The average delay under different computation workloads: (a) task arrival rate; (b) the number of MDs.}
	\label{chart3}
\end{figure}

\begin{figure}[tbp]
	\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.340\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ qoe_1} 		
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.340\linewidth}
		\includegraphics[width=\textwidth]{ qoe_2}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}
	%\vspace{-0.7cm}
	\caption{The average QoE under different computation workloads: (a) task arrival rate; (b) the number of MDs.}
	\label{chart4}
\end{figure}

In Fig.~\ref{chart2} (b), an increasing trend in overall energy consumption is observed as the number of MDs increases since the number of resources available in the system increases, which leads to higher energy consumption. The QECO algorithm consistently outperforms RD and PGOA methods in overall energy consumption, especially when there are a large number of MDs. Specifically, QECO demonstrates a 27\% and 16\% reduction in overall energy consumption compared to RD and PGOA, respectively, when the number of MDs increases to 110.

@@

%Fig. 6 illustrates a performance comparison of methods in terms of energy consumption in the entire system, considering an increase in the task arrival rate and the number of MDs. With efficient decision-making, the DRL-based algorithm achieves lower energy consumption in both cases compared to RD and PGOA. However, it consumes more energy compared to LC and FC. This is because LC only utilizes the MD's computational resources, and FC solely utilizes the transmission link. In Fig. 6(a), when the task arrival rate is low, the energy consumption of all methods is close to each other, and as the task arrival rate increases, the energy consumption of each method also increases. It can be observed that the generation of more computational tasks leads to a continuous increase in energy consumption. When the task arrival rate increases from 0.1 to 0.9, the DRL-based algorithm increases by 20\%, while RD and PGOA increase by at least 30\%. Similarly, in Fig. 6(b), the DRL-based algorithm effectively reduces energy consumption, especially when the number of MDs is large.The DRL-based algorithm demonstrates a 15\% reduction in energy consumption compared to RD and a 30\% reduction compared to PGOA as the number of MDs increases to 110.

@@

%The average QoE comparison in Fig.~\ref{chart4} (a) indicates the superiority of the QECO algorithm in providing MDs with a better experience. By taking into account the specific demands of MDs for each key performance metric, it consistently achieves a higher average QoE across various values of arrival task rates when compared to other methods. Specifically, when the task arrival rate is moderate (i.e., 250), QECO increases the average QoE by 57\% and 33\% compared to RD and PGOA, respectively. In Fig.~\ref{chart4} (b), As the number of MDs increases, the potential workload on the ENs also rises, leading to a decrease in the average QoE for each method (excluding LC). It can be observed that an increase in the ENs' workload leads to a reduction in the allocated computing capacity for MDs, resulting in a decrease in the average QoE. However, QECO effectively manages the uncertain load at the ENs. When the number of MDs increases to 90, it increases the average QoE by at least 29\% more than the other methods.

We further investigate the overall improvement achieved by the QECO algorithm in comparison to other methods in terms of the average QoE. This metric signifies the advantages MDs obtain by utilizing different algorithms. Fig.~\ref{chart4} (a) shows the average QoE for different values of task arrival rate. This figure indicates the superiority of the QECO algorithm in providing MDs with an enhanced experience. Specifically, when the task arrival rate is moderate (i.e., 250), QECO improves the average QoE by 57\% and 33\% compared to RD and PGOA, respectively. Fig.~\ref{chart4} (b) illustrates the average QoE when we increase the number of MDs. The EN's workload grows when there are a larger number of MDs, leading to a reduction in the average QoE of all methods except LC. However, QECO effectively manages the uncertain load at the ENs. When the number of MDs increases to 90, QECO achieves at least a 29\% higher QoE comparing with the other methods.
It is worth noting that although improvements in each of the QoE factors can contribute to enhancing system performance, it is essential to consider the user's demands in each time slot. Therefore, the key difference between QECO and other methods is that it prioritizes users' demands, enabling it to strike an appropriate balance among them, ultimately leading to a higher QoE for MDs.

@@

\begin{figure}
	\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.34\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ conv1_f} 
		\textcolor{white}{i}\hspace{0.4cm}(a)
	\end{minipage}
	\hspace{-0.26cm}
	\begin{minipage}[b]{0.34\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ conv2_f}
		\textcolor{white}{i}\hspace{0.4cm}(b)
	\end{minipage}

	\caption{The convergence of the average QoE across episodes under different hyper-parameters: (a) Learning rate; (b) Batch size.}
	\label{chart0}
\end{figure}

@@

(b) We have also revised the ralated works section, as below.\\

>>>>

	%In \cite{chen2019energy}, Chen \textit{et al.} introduced an online algorithm with polynomial time complexity for offloading in MEC. This algorithm achieves a close-to-optimal energy consumption while ensuring that the delay is bounded.

	%Liao \textit{et al.} in \cite{liao2023online} introduced a double reinforcement learning algorithm for performing online computation offloading in MEC. This algorithm optimizes transmission power and scheduling of CPU frequency to minimize both task computation delay and energy consumption. In \cite{huang2021deadline}, Huang \textit{et al.} proposed a DRL-based method based on a partially observable MDP, which guarantees the deadlines of real-time tasks while minimizing the total energy consumption of MDs. Liu  \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL, which can generate interactive information along with resource decisions. In \cite{chen2019energy}, Chen \textit{et al.} introduced an online algorithm with polynomial time complexity for offloading in MEC. This algorithm achieves a close-to-optimal energy consumption while ensuring that the delay is bounded. In \cite{dai2020edge}, Dai \textit{et al.} introduced the integration of action refinement into DRL and designed an algorithm to concurrently optimize resource allocation and computation offloading. Zhou \textit{et al.} in \cite{zhou2021deep} used an MDP to study MEC and modeled the interactions between the policy-system environment. They proposed a Q-learning approach to achieve optimal resource allocation strategies and computation offloading. Gong \textit{et al.} in \cite{gong2022edge} proposed a DRL-based network structure in the industrial internet of things system to jointly optimize task offloading and resource allocation, which can enable the system to achieve lower total cost of energy consumption and task delay. In \cite{gao2022large}, Gao \textit{et al.} introduced an attention-based multi-agent algorithm designed for decentralized computation offloading. This algorithm effectively tackles the challenges of dynamic resource allocation in large-scale heterogeneous networks.

@@

\begin{itemize}
	\item \textit{Task Offloading Problem in the MEC System:} \textcolor{purple}{ We formulate the task offloading problem in queuing-based MEC as an MDP for time-sensitive tasks, taking into account the time-varying system environments (e.g., the arrival of new tasks, and the computational requirement of each task). This approach concentrates on providing high performance in the MEC system while maximizing the long-term QoE, by effectively utilizing the capabilities of resources and handling the dynamic nature of workload at ENs.}

	\item \textit{DRL-based Offloading Algorithm:} To address the problem of long-term QoE maximization, we focus on task completion, task delay, and energy consumption to quantify the MDs' QoE. We propose QECO algorithm based on DRL that empowers each MD to make offloading decisions independently, without prior knowledge of the other MDs' tasks and offloading models. \textcolor{purple}{With a focus on the MD's energy level, our approach leverages dueling double deep Q-network (D3QN) \cite{wang2016dueling} to prioritize and strike an appropriate balance between QoE factors. To handle the uncertainty of workloads at ENs, we integrate long short-term memory (LSTM) \cite{hochreiter1997long} into D3QN, enabling MDs to forecast ENs' workloads over time and improve the estimation of long-term QoE. Additionally, we provide an analysis of the training convergence and computational complexity of the proposed algorithm.}

	\item \textit{Performance Evaluation:} \textcolor{blue}{We conducted comprehensive experiments to evaluate QECO's performance under various computational workloads, as well as its training convergence with different techniques and hyperparameters. The results demonstrate that our algorithm effectively utilizes the processing capabilities of MDs and ENs, addressing the dynamic workloads at ENs. It converges more quickly compared to DQN and D3QN methods, while providing a substantial improvement of at least 34.8\% in average QoE. This advantage is achieved through prioritizing MD's QoE preferences, resulting in improvements of at least 12.2\%, 11.7\%, and 10.8\% in the average number of completed tasks, task delay, and energy consumption, respectively, when compared to the distributed and collective DRL-based offloading algorithm (DCDRL) \cite{qiu2020distributed} and several benchmark methods.}

@@

\section{System Model} 
\label{section:II}
\label{sec:latexhints}
% Required for proper example rendering in the compiled PDF
\newcount\LTGbeginlineexample
\newcount\LTGendlineexample
\newenvironment{ltgexample}%
{\LTGbeginlineexample=\numexpr\inputlineno+1\relax}%
{\LTGendlineexample=\numexpr\inputlineno-1\relax%
	%
	\tcbinputlisting{%
		listing only,
		listing file=\currfilepath,
		colback=green!5!white,
		colslot=green!25,
		coltitle=black!90,
		coltext=black!90,
		left=8mm,
		title=Corresponding \LaTeX{} code of \texttt{\currfilepath},
		listing options={%
			slot=none,
			language={[LaTeX]TeX},
			escapeinside={},
			firstline=\the\LTGbeginlineexample,
			lastline=\the\LTGendlineexample,
			firstnumber=\the\LTGbeginlineexample,
			basewidth=.5em,
			aboveskip=0mm,
			belowskip=0mm,
			numbers=left,
			xleftmargin=0mm,
			numberstyle=\tiny,
			numbersep=8pt%
		}
	}
}%
We investigate a MEC system consisting of a set of MDs denoted by $\mathcal{I} = \{1, 2, ..., I\}$, along with a set of ENs denoted by $\mathcal{J} = \{1, 2, ..., J\}$, where $I$ and $J$ represent the number of MDs and ENs, respectively. We regard time as a specific episode containing a series of $T$ time slots denoted by $\mathcal{T} = \{1, 2, \ldots, T\}$, each representing a duration of $\tau$ seconds. As shown in Fig.~\ref{fig1}, we consider two separate queues for each MD to organize tasks for local processing or dispatching to ENs, operating in a first-in-first-out (FIFO) manner. The MD's scheduler is responsible for assigning newly arrived tasks to each of the queues at the beginning of the time slot. On the other hand, we assume that each EN $j \in \mathcal{J}$ consists of $I$ FIFO queues, where each queue corresponds to an MD $i \in \mathcal{I}$. When each task arrives at an EN, it is enqueued in the corresponding MD's queue. %We assume that if a task is completed in a certain time slot, the next task in the queue will start its operation at the beginning of the next time slot.
%
\begin{figure}
	\captionsetup{name=Fig.}
	\centering
	\includegraphics[width=.7\linewidth]{ queue}
	\vspace*{-1mm}
	\caption{An illustration of MD $i \in \mathcal{I}$ and EN $j \in \mathcal{J}$ in the MEC system.}
	\vspace*{-3mm}
	\label{fig1}
\end{figure}

@@

%\begin{figure}
%	\centering
%	\includegraphics[width=0.7\linewidth]{ DQN}
%	\captionsetup{name=Fig.}
%	
%	\caption{The neural network of MD $i \in \mathcal{I}$, which characterize the Q-value of each action $\boldsymbol{a} \in \mathcal{A}$ under state $\boldsymbol{s}_i(t) \in \mathcal{S}$.}
%	\vspace*{-4.5mm}
%	\label{DQN}
%\end{figure}

@@

discover the optimal offloading policy. Each experience involves backpropagation for training, which has a computational complexity of $\mathcal{O}(C)$, where $C$ represents the number of multiplication operations in the neural network. During each training round triggered by the arrival of a new task, a sample collection of experiences of size $|\mathcal{N}|$ is utilized from the replay buffer. Since the training process encompasses $N^{\text{ep}}$ episodes and there are $K$ expected tasks in each episode, the computational complexity of the proposed algorithm is $\mathcal{O}(N^{\text{ep}}K|\mathcal{N}|C$), which is polynomial. Given the integration of neural networks for function approximation, the convergence guarantee of the DRL algorithm remains an open problem. In this work, we will empirically evaluate the convergence of the proposed algorithm in Section \ref{section:2}.

@@

	\item \textbf{DCDRL~\cite{yang2018distributed}:} This existing method is a distributed optimization algorithm designed for delay-sensitive tasks in an environment where MDs interact strategically with multiple ENs. We select DCDRL as a benchmark method due to its similarity to our work.
\end{enumerate}

@@

%This represents a notable enhancement of 77\% and 16\% over LC and DCDRL, respectively. This improvement is attributed to our algorithm's ability to reduce each user-associated cost regarding \eqref{28}, while striving to increase the number of completed tasks. As shown in Figs. \ref{chart0} (b), the converged QECO algorithm decreases the average cost by 38\% compared to RD and 25\% compared to DCDRL.

@@

We first evaluate the number of completed tasks when comparing our proposed QECO algorithm with the other four schemes. As illustrated in Fig.~\ref{chart1} (a), the QECO algorithm consistently outperforms the benchmark methods when we vary the task arrival rate. At a lower task arrival rate (i.e., 50), most of the methods demonstrate similar proficiency in completing tasks. However, as the task arrival rate increases, the efficiency of QECO becomes more evident. Specifically, when the task arrival rate increases to 250, our algorithm can increase the number of completed tasks by 73\% and 47\% compared to RD and DCDRL, respectively.
Similarly, in Fig.~\ref{chart1} (b), as the number of MDs increases, QECO shows significant improvements in the number of completed tasks compared to other methods, especially when faced with a large number of MDs. When there are 110 MDs, our proposed algorithm can effectively increase the number of completed tasks by at least 34\% comparing with other methods. This achievement is attributed to the QECO's ability to effectively handle unknown workloads and prevent congestion at the ENs.

Figs.~\ref{chart2} (a) and ~\ref{chart2} (b) illustrate the overall energy consumption for different values of task arrival rate and the number of MDs, respectively. At the lower task arrival rate, the total energy consumption of all methods is close to each other. The total energy consumption increases when we have a higher task arrival rate.  
%When the task arrival rate increases, the total energy consumption of each method increases differently. It can be found that the production of more computational tasks leads to a continuous increase in energy consumption until the capacity is saturated, and the energy consumption remains constant at its maximum. The QECO algorithm takes into account the battery level of the MD in its decision-making process. 
As can be observed from Fig.~\ref{chart2} (a), at task arrival rate 450, QECO effectively reduces overall energy consumption by 18\% and 15\% compared to RD and DCDRL, respectively, as it takes into account the battery level of the MD in its decision-making process. However, it consumes more energy compared to LC and FO because they do not utilize all computing resources. In particular, LC only uses the MD's computational resources, while FO utilizes the allocated EN computing resources.

%\begin{figure}[tbp]
%	\centering
%	\captionsetup{name=Fig.}
%	\begin{minipage}[b]{0.34\linewidth}
%		\centering
%		\includegraphics[width=\textwidth]{ completed_tasks_1} 
%		\textcolor{white}{i}\hspace{0.6cm}(a)
%	\end{minipage}
%	\hspace{-0.2cm}
%	\begin{minipage}[b]{0.34\linewidth}
%		\centering
%		\includegraphics[width=\textwidth]{ completed_tasks_2}
%		\textcolor{white}{i}\hspace{0.6cm}(b)
%	\end{minipage}
%	%\vspace{-0.65cm}
%	\caption{The number of completed tasks under different computation workloads: (a) task arrival rate; (b) the number of MDs.}
%	\label{chart1}
%\end{figure}
%
%
%
%\begin{figure}[tbp]
%	\centering
%	\captionsetup{name=Fig.}
%	\begin{minipage}[b]{0.340\linewidth}
%		\centering
%		\includegraphics[width=\textwidth]{ energy_1} 		
%		\textcolor{white}{i}\hspace{0.6cm}(a)
%	\end{minipage}
%	%\hspace{-0.2cm}
%	\begin{minipage}[b]{0.340\linewidth}
%		\centering
%		\includegraphics[width=\textwidth]{ energy_2}
%		\textcolor{white}{i}\hspace{0.6cm}(b)
%	\end{minipage}
%	%\vspace{-0.7cm}
%	\caption{The overall energy consumption under different computation workloads: (a) task arrival rate; (b) the number of MDs.}
%	\label{chart2}
%\end{figure}
%
%\begin{figure}[t]
%	\centering
%	\captionsetup{name=Fig.}
%	\begin{minipage}[b]{0.340\linewidth}
%		\centering
%		\includegraphics[width=\textwidth]{ delay_1} 		
%		\textcolor{white}{i}\hspace{0.6cm}(a)
%	\end{minipage}
%	\hspace{-0.2cm}
%	\begin{minipage}[b]{0.340\linewidth}
%		\centering
%		\includegraphics[width=\textwidth]{ delay_2}
%		\textcolor{white}{i}\hspace{0.6cm}(b)
%	\end{minipage}
%	%\vspace{-0.7cm}
%	\caption{The average delay under different computation workloads: (a) task arrival rate; (b) the number of MDs.}
%	\label{chart3}
%\end{figure} 
%
%\begin{figure}[tbp]
%	\centering
%	\captionsetup{name=Fig.}
%	\begin{minipage}[b]{0.340\linewidth}
%		\centering
%		\includegraphics[width=\textwidth]{ qoe_1} 		
%		\textcolor{white}{i}\hspace{0.6cm}(a)
%	\end{minipage}
%	\hspace{-0.2cm}
%	\begin{minipage}[b]{0.340\linewidth}
%		\includegraphics[width=\textwidth]{ qoe_2}
%		\textcolor{white}{i}\hspace{0.6cm}(b)
%	\end{minipage}
%	%\vspace{-0.7cm}
%	\caption{The average QoE under different computation workloads: (a) task arrival rate; (b) the number of MDs.}
%	\label{chart4}
%\end{figure}

In Fig.~\ref{chart2} (b), an increasing trend in overall energy consumption is observed as the number of MDs increases since the number of resources available in the system increases, which leads to higher energy consumption. The QECO algorithm consistently outperforms RD and DCDRL methods in overall energy consumption, especially when there are a large number of MDs. Specifically, QECO demonstrates a 27\% and 16\% reduction in overall energy consumption compared to RD and DCDRL, respectively, when the number of MDs increases to 110.

@@

%Fig. 6 illustrates a performance comparison of methods in terms of energy consumption in the entire system, considering an increase in the task arrival rate and the number of MDs. With efficient decision-making, the DRL-based algorithm achieves lower energy consumption in both cases compared to RD and DCDRL. However, it consumes more energy compared to LC and FC. This is because LC only utilizes the MD's computational resources, and FC solely utilizes the transmission link. In Fig. 6(a), when the task arrival rate is low, the energy consumption of all methods is close to each other, and as the task arrival rate increases, the energy consumption of each method also increases. It can be observed that the generation of more computational tasks leads to a continuous increase in energy consumption. When the task arrival rate increases from 0.1 to 0.9, the DRL-based algorithm increases by 20\%, while RD and DCDRL increase by at least 30\%. Similarly, in Fig. 6(b), the DRL-based algorithm effectively reduces energy consumption, especially when the number of MDs is large.The DRL-based algorithm demonstrates a 15\% reduction in energy consumption compared to RD and a 30\% reduction compared to DCDRL as the number of MDs increases to 110.

@@

%The average QoE comparison in Fig.~\ref{chart4} (a) indicates the superiority of the QECO algorithm in providing MDs with a better experience. By taking into account the specific demands of MDs for each key performance metric, it consistently achieves a higher average QoE across various values of arrival task rates when compared to other methods. Specifically, when the task arrival rate is moderate (i.e., 250), QECO increases the average QoE by 57\% and 33\% compared to RD and DCDRL, respectively. In Fig.~\ref{chart4} (b), As the number of MDs increases, the potential workload on the ENs also rises, leading to a decrease in the average QoE for each method (excluding LC). It can be observed that an increase in the ENs' workload leads to a reduction in the allocated computing capacity for MDs, resulting in a decrease in the average QoE. However, QECO effectively manages the uncertain load at the ENs. When the number of MDs increases to 90, it increases the average QoE by at least 29\% more than the other methods.

We further investigate the overall improvement achieved by the QECO algorithm in comparison to other methods in terms of the average QoE. This metric signifies the advantages MDs obtain by utilizing different algorithms. Fig.~\ref{chart4} (a) shows the average QoE for different values of task arrival rate. This figure indicates the superiority of the QECO algorithm in providing MDs with an enhanced experience. Specifically, when the task arrival rate is moderate (i.e., 250), QECO improves the average QoE by 57\% and 33\% compared to RD and DCDRL, respectively. Fig.~\ref{chart4} (b) illustrates the average QoE when we increase the number of MDs. The EN's workload grows when there are a larger number of MDs, leading to a reduction in the average QoE of all methods except LC. However, QECO effectively manages the uncertain load at the ENs. When the number of MDs increases to 90, QECO achieves at least a 29\% higher QoE comparing with the other methods.
It is worth noting that although improvements in each of the QoE factors can contribute to enhancing system performance, it is essential to consider the user's demands in each time slot. Therefore, the key difference between QECO and other methods is that it prioritizes users' demands, enabling it to strike an appropriate balance among them, ultimately leading to a higher QoE for MDs.

@@

%\begin{figure}
%	\centering
%	\captionsetup{name=Fig.}
%	\begin{minipage}[b]{0.34\linewidth}
%		\centering
%		\includegraphics[width=\textwidth]{ conv1_f} 
%		\textcolor{white}{i}\hspace{0.4cm}(a)
%	\end{minipage}
%	\hspace{-0.26cm}
%	\begin{minipage}[b]{0.34\linewidth}
%		\centering
%		\includegraphics[width=\textwidth]{ conv2_f}
%		\textcolor{white}{i}\hspace{0.4cm}(b)
%	\end{minipage}
%
%	\caption{The convergence of the average QoE across episodes under different hyper-parameters: (a) Learning rate; (b) Batch size.}
%	\label{chart0}
%\end{figure}

@@

(b) We have also revised the ralated works Section, as below.\\
